---
title: "Assignment 2"
author: "Joyce Wu(5897736) & Yen-Chen Hsu(5897444)"
date: "2023-10-01"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Maximizing ROI: A Comprehensive Analysis of Effective Advertising Strategy for Star Digital

This is an analysis to measure causal effect of display advertising on
sales conversion. We are interesting in finding out both a) is the
advertising effective and b) which site(s) should Star Digital advertise
on if it is in fact effective.

In our analysis, we examined two key aspects: the impact of advertising
on the likelihood of purchase and the cost-effective channel of our
advertising sites. Our analysis demonstrates that increasing the
frequency of advertising impression positively affect probability of
purchase. Additionally, the data suggests that Site 6 is the preferred
platform for advertising due to its potential of delivering a higher
ROI. These insights should guide Star Digital in optimizing its display
advertising strategy to improve effectiveness and return on investment.

```{r}
library(dplyr)
library(readxl)
library(ggplot2)
```

### Analysis Detail

#### Loading data set for analysis

```{r}
#star<-read_excel("/Users/joycewu/Library/CloudStorage/GoogleDrive-wu001370@umn.edu/My Drive/Fall/Inference/Assignment 2/Star Digital Dataset.xls", na="NA", col_names = TRUE)
```

1.  Descriptive Statistic:

    First, let's look at the structure and summary of the data:

```{r}
print(summary(star))
print(str(star))
```

In order to understand more about the distribution of 6 websites from
the experiment, we plot out the IQR plot for each website.

```{r}
#imp_1~imp_6 stands for the number of ad impression for either Star Digital or charity
Q1 <- apply(star[, 4:9], 2, quantile, probs=0.25)
Q3 <- apply(star[, 4:9], 2, quantile, probs=0.75)
IQR_values <- Q3 - Q1

# Identify potential outliers
lower_bound <- Q1 - 1.5 * IQR_values
upper_bound <- Q3 + 1.5 * IQR_values

# Create box plots for imp_1 to imp_6
par(mfrow=c(2, 3))  # Set up a 2x3 grid for multiple box plots
for (i in 4:9) {
  boxplot(star[, i], main=paste("Box Plot of", colnames(star)[i]), outline=FALSE)
}
```

```{r}
# Create box plot for imp_1 to imp_6
boxplot(star[, 4:9], main="Boxplots of imp_1 to imp_6")
```

From above plots, we observed that the variables 'imp_2' and 'imp_6'
displayed a notably higher number of outliers compared to the other
websites. If possible, management team should also dive in the nature of
these outliers in website 2 & 6, to find out what causes more impression
to happen on these sites.

Then, we proceed to assess the result of the experiment. The measurable
objective in the data set will be "purchase", hence, we would calculate
the ad impression to purchase rate and unique user purchase rate.

```{r}
star = star %>% mutate(total_imp = imp_1+imp_2+imp_3+imp_4+imp_5+imp_6)

#unique ID to purchase rate
purchase_count <- sum(star$purchase == 1)
total_records <- nrow(star)
purchase_rate_uuid <- purchase_count/total_records
cat("purchase per unique ID: ", purchase_rate_uuid)
```

```{r}
#impression-to-purchase rate
impression_to_purchase_rate <- purchase_count / sum(star$total_imp)
cat("Impression-to-Purchase Rate:", impression_to_purchase_rate)
```

2.  Randomization check: Here, we use t.test to understand if test and
    control groups are randomly given treatment by assessing whether
    total_imp varies across 2 groups. #small p-value = different H0 =
    not difference in total impression between test and control group;
    H1 = there's difference of total impression between test and control
    group)

```{r}
t.test(total_imp ~ test, star)
```

From t.test result, we report p-value 0.8987, which is quite high,
indicating that there is not enough evidence to reject the null
hypothesis. In other words, based on the data and the statistical test
performed, it does not appear that there is a significant difference in
the "total_imp" between control and test group

We conducted a randomization check to impression on Site 1 through 5 as
well as on Site 6. We can also conclude that there is no significant
differences between the number of impressions for these 2 grouped Sites
between the control and test group.

```{r}
# sum total impression on Site 1 through 6
star = star %>% mutate(site15_imp = imp_1+imp_2+imp_3+imp_4+imp_5)
t.test(site15_imp ~ test, star)
```

```{r}
t.test(imp_6 ~ test, star)
```

3.  Sample Size check:

```{r}
power.t.test(delta=.1, sd = 1, sig.level = .05, power = 0.8, type = "two.sample",alternative = "two.sided")
```
Alternative way to find d with given n
```{r}
power.t.test(d=NULL, n = 2656, sd = 1, sig.level = .05, power = 0.8, type = "two.sample",alternative = "two.sided")
```

Given the management team's goal of boosting the purchase conversion
rate by 1% with the intervention, we set the delta as 0.1, and the
minimum sample size for control and test group should be around 1570. We
have a big enough sample size for both groups.

**`Question 1 - Is online advertising effective for Star Digital?`**

```{r}
summary(lm(purchase ~ test, star))
```

From the above regression, we can obtain the p-value for 'test' as
0.0614, greater than the acceptable significance level of 0.05. This
indicates that we do not have enough evidence to reject the null
hypothesis: the experiment of displaying Star Digital ads to the test
group has no effect on their purchase behavior. We should also note that
the sample data set was deliberately chosen, we should not arbitrarily
conclude that the ad display experiment is useless.

Although we did not have sufficient evidence to support the experiment's
effectiveness, we did observe a positive correlations between the test
group and the average number of purchases increase by 1.91%.

**`Question 2 - Whether increasing frequency of advertising increases the probability of purchase?`**

To answer this question, we would first inspect the impression frequency
of test and control group.

```{r}
summary(lm(purchase ~ test*total_imp, data = star))
```

To discuss the effectiveness of impression frequency on the probability
of purchase, we can refer to the p-value of the total impression and the
interaction of the test and total impression. Both of them demonstrate
very small p-values, much lower than the significant level 0.05: .3.49e
-10 for total impression, and 0.0188 for the interaction of total
impression and test.

This indicates that we have enough evidence to reject the null
hypothesis, in other words, the total impression number does effects
number of purchases.

The output also provides insight into how purchase event changes for a
one unit increase of impression. A one unit increase in 'total_imp' is
associated with an estimated increase of approximately 0.0025937 in the
purchase. Furthermore, given the positive interaction effect of total
impression and the test, we can know that for the test group as total
impression increase, the purchase increases simultaneously.

**`Question 3 - Which site should Star Digital advertise on? (Site 6 or in Site 1 through 5)`**

Here we present a short summary table of the number of users, purchases,
impression on Site 6 or on Site 1 through 5 in order to get a clearer
sense of the total ROI for both the test and control groups.

```{r}
star %>% group_by(test) %>% summarize(count_users = n(), 
                                      total_purchase = sum(purchase),
                                      total_imp = sum(total_imp), 
                                      total_6imp = sum(imp_6),
                                      total_15imp = sum(site15_imp),
                                      cost = (25*(total_15imp/1000)+
                                                20*(total_6imp/1000)),
                                      revenue = (1200*total_purchase),
                                      ROI = ((revenue-cost) / cost))
```

For this question, we will only like to see the correlation of the
impressions with purchases for the testing group. We will filter this
subset of data, and focus on observing the difference in effectiveness
between impressions on Site 1 through 5 versus impression on Site 6.

```{r}
star_test = star %>% filter(test == 1) %>% mutate(site15_imp = imp_1+imp_2+imp_3+imp_4+imp_5)
```

Next, we run an model to test the correlation between the total
impression on Site 1 through 5 and purchases. The result of this model
shows a statistical significance of a positive correlation where
purchases increase around 0.0039 with one unit increase of impression on
Site 1 through 5.

```{r}
summary(lm(purchase ~ site15_imp, data = star_test))
```

We did the same analysis to observe the correlation between the total
impression on Site 6 and purchases. The result shows a statistical
significance of a positive correlation where purchases increase around
0.0037 with one unit increase of impression on Site 6.

```{r}
summary(lm(purchase ~ imp_6, data = star_test))
```

Here is a tabular summary of how impression of both Site 1 through 5
versus Site 6 has on ROI taking into account the unit price per
impression as well as the expected revenue increase in dollar amount. In
summary, we would recommend Star Digital advertise more on Site 6 than
on Site 1 through 5, due to a higher expected ROI yield.

```{r}
table = data.frame(
  Site = c("Site_1-5", "Site_6"),
  Revenue_per_impression_increase = c("0.0038981*$1200 = $4.67", "0.0036950*$1200 = $4.43"),
  Cost_per_impression = c("$0.025", "$0.020"),
  ROI_per_impression_increase = c("185.8","220.5")
)
print(table)
```
